In this thesis, we will explore various methods for measuring \gls{emg} and \gls{eda} simultaneously.
 %Dual biosignal acquisition - Passive and Active
\section{Background and Motivation}
The motivation for this thesis is based on the research article "\textit{Using heart rate monitoring to discover pain and discomfort in non-verbal persons with severe intellectual disability: Caregivers' experiences}" \cite{boysen_using_2024}. In the research article, the authors conducted a clinical study to determine whether heart rate (HR) monitoring could help caregivers identify pain and discomfort in non-verbal individuals with severe intellectual disabilities. They found that the benefits experienced varied among participants, depending on the specific study circumstances and the individual's level of activity. In collaboration with the Department of Clinical and Biomedical Engineering at Oslo University Hospital (OUS), this thesis was proposed. The objective is to investigate whether electrodermal activity (EDA) and electromyography (EMG) can also serve as biological markers for detecting pain or discomfort. This thesis aims to explore this possibility. 

In recent years, it has been observed that studies utilizing multiple signals simultaneously can potentially enhance the performance of assessment models by increasing their accuracy and specificity \cite{mcnaboe_design_2022}. To my knowledge, measuring electrodermal activity (EDA) and electromyography (EMG) simultaneously on the same muscle has never been attempted. While previous studies have successfully measured EDA and electrocardiogram (ECG) activity concurrently \cite{mohaddes_simultaneous_2021}, there have been earlier studies that measured EMG, EDA, and ECG simultaneously, but not from the same reference points on the body.\cite{mcnaboe_design_2022}. 


\section{Objectives}

\section{Thesis Outline}
This thesis is divided into six sections:
\begin{itemize}
    \item Chapter 1 serves as an introduction, providing background information on the motivation for the simultaneous measurement of EDA (Electrodermal Activity) and EMG (Electromyography), as well as the objectives of this thesis.
    \item Chapter 2 discusses the theoretical framework that underpins this research. It will explain the basic physiology of the human body, the relevance of these physiological aspects to EDA and EMG measurement methods, and offer an in-depth exploration of the various measurement techniques.
    \item Chapter 3 outlines the methods employed in this study.
    \item Chapter 4 presents the results obtained from the research.
    \item Chapter 5 contains a comprehensive discussion of the results.
    \item Chapter 6 summarizes the key findings and suggests directions for future work.
\end{itemize}
\begin{itemize}
    \item Historical background
    \item Identify knowledge gap
    \item Explain why this work is needed (Motivation)
    \item Explain what is coming in the thesis
    \item Start early but finish last
\end{itemize}