\section{Filters}

\section{Galvanic Isolation}

\section{Research Protocol}
\subsection{Aim}
To validate a custom circuit for simultaneous measurement of surface EMG and EDA from the same muscle area. 

\subsection{Validation questions}
\begin{enumerate}
    \item Can EMG activity be recorded without saturating or distorting the EDA signal?
    \item Can EDA activity be recorded without saturating or distorting the EMG signal?
    \item Is the EMG signal-to-noise ratio acceptable during EDA responses?
    \item Does the circuit allow clear detection of known, reproducible EMG and EDA responses?
\end{enumerate}

\subsection{Participants}
One healthy adult (the author), right-handed, with no known neuromuscular or dermatological disorders affecting the hands.
This is a technical self-experiment conducted solely for circuit validation. 

\subsection{Equipment and setup}
\begin{itemize}
    \item Custom-made EMG/EDA circuit (see circuit diagram in Figure~X.Y).
    \item Electrodes: Kendall EMG Snap-On Electrodes
    \begin{itemize}
        \item Type: H135SG, Ref: 31.1355.21
        \item Material: Ag/AgCl
        \item Size: 43 $\times$ 35 mm
        \item Disposable, pre-gelled
    \end{itemize}
    \item Data acquisition card: NI USB-6356 DAQ
    \begin{itemize}
        \item Sampling rate: $f_s = 2000$ Hz on all channels
        \item Connected to a PC running Python 3.10.4 using the \texttt{nidaqmx} package
    \end{itemize}
    \item UNI-T UT131B multimeter
    \item Force-sensitive resistor: Interlink Electronics FSR402
    \begin{itemize}
    \item Resistance range: \SI{200}{\ohm} (maximum pressure) to
          \SI{100}{\kilo\ohm} (light pressure)
    \item Connected to a multimeter in resistance mode
    \end{itemize}
    \item Environment:
    \begin{itemize}
        \item Quiet room, normal indoor lighting
        \item Room temperature approximately 21--24 $^\circ$C
        \item All recordings performed between 09:00 and 12:00
    \end{itemize}
\end{itemize}

\subsection{Electrode placement and skin preparation}

\subsubsection{Skin preparation}
The participant washes both hands with soap and water and dries them thoroughly with a paper towel.
No lotion, cream, or skin products are applied to the hands or wrists on the morning of the recording.
Jewelry is removed from the left hand and wrist.

\subsubsection{Electrode placement}
Three electrodes are used for EMG and two for EDA (Figure is coming later).

For EMG, two recording electrodes are placed over the thenar eminence of the left hand in a bipolar configuration.
The electrodes are aligned approximately along the proximal--distal axis of the thumb musculature, with an inter-electrode distance of 10~mm (edge-to-edge).
The EMG reference electrode is placed on the dorsal aspect of the left forearm, approximately 5~cm distal to the elbow.

For EDA, two electrodes are placed on the palmar surface over the lumbrical region between the index and middle fingers of the left hand, with a center-to-center distance of approximately 10 mm.
These electrodes are used in a standard conductance configuration.

%Revised version
\begin{comment}
Three electrode configurations are tested across sessions:

\textbf{Configuration A (original):} Two EMG recording electrodes over the
thenar eminence in bipolar configuration, aligned along the proximal--distal
axis with 10\,mm edge-to-edge separation. Two EDA electrodes over the
lumbrical region between the index and middle fingers.

\textbf{Configuration B (supervisor suggestion, left):} One EMG electrode
placed over the muscle belly (largest thenar mass) and one more distally on
the proximal thumb phalanx, mimicking a clinical CMAP recording arrangement.
Two EDA electrodes placed over the hypothenar eminence (a well-established
EDA measurement site. This configuration maximises expected EMG amplitude
and spatially separates EMG and EDA electrode fields.

\textbf{Configuration C (supervisor suggestion, right):} EMG electrodes
positioned within the current path between the two EDA electrodes, to
stress-test whether cross-interference occurs under the worst-case spatial
overlap.
\end{comment}

\subsection{Outcome measures and success criteria}

\begin{itemize}
    \item Signal quality
    \item Minimal interference
    \item Reproducibility
\end{itemize}

(Discuss with supervisors what requirements to have)

\subsection{Step-by-step procedure}

\subsubsection{Stimulation instructions}

\paragraph{EMG stimulation}
The participant sits with the left forearm resting on the table, elbow flexed approximately 90$^\circ$, and the palm facing up.
The fingers are relaxed in a neutral, slightly open position. An FSR is placed between the thumb and little finger before the block begins and remains in position throughout.

% Double-check the resistor value
At each EMG stimulus cue, the participant performs a thumb--little finger opposition movement by bringing the thumb tip into contact with the tip of the little finger as quickly as possible and then maintaining a moderate contraction for 2 seconds. The participant is instructed to apply sufficient force to bring the FSR resistance to approximately \SI{1}{\kilo\ohm}, which serves as the target contraction level and corresponds to approximately 30\% of perceived maximal effort. The resistance across the FSR is noted at peak contraction. After 2 seconds, the participant relaxes the hand and returns to the neutral position.

\paragraph{EDA stimulation}
At each EDA stimulus cue, the participant inhales deeply over 2 seconds, starting from normal breathing, then exhales normally and relaxes.
The timing of the deep breath is guided by a visual or auditory cue generated by the control software.

\subsubsection{Recording procedure}
Each recording session consists of one test run of three consecutive 10-minute blocks (EDA-only, EMG-only, combined), preceded by a resting period.

\begin{enumerate}
    \item The participant sits on a chair with both feet flat on the ground and the back supported.
    \item EMG and EDA electrodes are applied to the left hand and forearm as described above.
    \item After electrode placement, the participant rests quietly for 30 minutes to allow stabilization of electrode-skin impedance.
    \item During the final 10~minutes of this period, baseline EMG and EDA signals are recorded while the participant remains still and breathes normally.
    \item The 30-minute test run then begins, consisting of three 10-minute blocks:
    \begin{enumerate}
        \item \textbf{Block 1: EDA-only (10 minutes)}\\
        The participant remains seated with the left hand resting in the neutral position.
        Every 60 seconds, a cue prompts the participant to perform one deep-breath EDA stimulus as described above.
        No voluntary hand or finger movement is performed other than what is minimally required for comfortable breathing.
        This block yields 10 EDA stimuli.
        \item \textbf{Block 2: EMG-only (10 minutes)}\\
        The participant continues to sit in the same position.
        Every 15~seconds, a cue prompts the participant to perform one EMG stimulus (thumb--little finger opposition) for 2~seconds, followed by relaxation.
        Normal quiet breathing is maintained, and no deep-breath EDA stimuli are performed.
        This block yields 40 EMG stimuli.
        \item \textbf{Block 3: Combined EMG + EDA (10 minutes)}\\
        The participant performs both types of stimuli according to the same timing as in Blocks 1 and 2.
        Deep-breath EDA stimuli are performed every 60~seconds, and EMG stimuli are performed every 15~seconds.
        This block yields 10 EDA stimuli and 40 EMG stimuli.
    \end{enumerate}
    \item In total, one test run yields 20 EDA stimuli (10 in EDA-only + 10 in combined) and 80 EMG stimuli (40 in EMG-only + 40 in combined).
    \item The complete test run is repeated on two additional days under the same conditions, for a total of three sessions on three separate days.
    \item Before Block 2, the participant performs three maximum-effort thumb--little finger oppositions against the FSR to establish an individual maximum resistance reading. During EMG stimuli, the participant is instructed to target approximately 30\% of maximum effort. The FSR resistance is noted at peak contraction in each trial to verify consistency across stimuli and sessions.
\end{enumerate}

%Linear Envelope Detection is the most commonly applied demodulation technique used to extract information from the observed EMG waveform.
\begin{itemize}
    \item Describe the methods you use
    \item History
    \item Background
    \item Advantages
    \item Limitations
    \item Applications
    \item What's new?
\end{itemize}

\begin{itemize}
    \item Specifications
    \item Why I chose DC EDA
    \item How does it affect the EMG
    
\end{itemize}